% -------- Projects --------------------------------------------
\begin{category}{Projects}
\citem{Music recommender system [2016]} A personal music recommender system using user preference analysis. I used hybrid model approach which is a combination of collaborative and content based filtering. Apart from recommender system I also build a automatic genre classifier. I used Apache spark(map-reduce) for processing large data-set and Mlib(part of spark) for constructing a model.
\citem{pyFFT [2016]} The python implementation of Fast Fourier transformations and Discrete Fourier transformations.
\citem{YPOD [2016]} The YPOD is an embedded-systems platform developed at the University of Colorado at Boulder intended for mobile air quality and environmental monitoring. The configurable design accommodates a variety of sensors, making it a valuable tool for a multitude of applications.
\citem{Betrayal in On-line Strategy Game Diplomacy [2015]} Detecting when the betrayal is going to happen in a on-line strategy game called Diplomacy. Our approach involves using the game state to capture the game contextual information for modelling a classifier.
\citem{Distributed File Server [2015]} Client/server based application that allows client to store and retrieve files from multiple servers. Support for simultaneous multiple users, authentication and data encryption using AES.
\citem{Web server [2015]} Implementation of HTTP web server in C++11. Supports handling of multiple clients, HTTP 1.0 and HTTP 1.1, persistent connection(pipe-lining). Brings up the web server based on the web configuration file.
\citem{Key logger [2015]} This is a winter break free-time project. The idea is to track the user keystrokes. It's a client server based architecture. Where the client runs in the background without the knowledge of the user, started as a demon at kernel boot time. This client will listen to the keys and send the window name, user id and keystroke to the server.
\citem{Screen Recorder [2014]} Screen recorder records all screen activity on your computer and create a video file using FFMPEG encoder. It is written in C\#. It let's you save the video in the required format (MP4, AVI, MKV etc.).
\citem{.NET Memory Profiler [2014]} A custom .NET memory profiler application. It automatically logs the memory consumption for the process/processes which has loaded the module(DLL) of interest in Syngo.Via application. This profiler helped in figuring out the memory leaks and Out of memory exception in the project.
\citem{Simple OS [2013]} A simple Linux like operating system written in C and Assembly using GRUB boot loader.
\citem{Voice over GPRS [2010]} Voice over GPRS is a Voice chat application for symbian mobile phones. It consisted of 3 subsystems Voice chat, Voice-mail and Virtual classroom.
\end{category}
