\documentclass{coverletter}
\usepackage{ragged2e}
\begin{document}

\begin{letterheader}
\name{Sunil BN}
\homeaddress{
2995 Glenwood Dr \\
& Boulder, CO 80301\\
& United States \\
}

\companyaddress{
University of Colorado, Boulder & \\
}
\end{letterheader}

\begin{letter}
\subject{Application for Graduate internship programme at Siemens Medical solutions.}
\greet{To whom this may concern}
%\greet{Dear Salim}
\begin{content}

I’m a graduate student doing my masters in computer science. My areas of interest are data science (Machine learning), statistics and Algorithms. Currently I’m working under Prof. Michael Hannigan from the Department of Mechanical engineering writing Firmware for the UPOD(Arduino Yun and sensors), a low-cost air quality monitoring platform (http://mobilesensing-technology.com/).\\\\
Before beginning my graduate studies, I worked as an associate engineer – Design and development in Siemens for 4 years. I am of the opinion that I will be an asset to any team that I work with.\\\\
I have graduate GPA of 4.0/4.0 and an undergraduate GPA of 3.67/4.0(80.44\%). I have actively assisted professors by giving seminars to the class in computer science subjects on a voluntary basis. After obtaining my undergraduate degree I worked in the Research and Development wing of Siemens Healthcare. Over a span of 4 years of experience I have learnt and worked on latest computer technologies. In the projects apart from designing and development of the software, I was also responsible for analysing and fixing non-functional requirements like performance and memory constraints.\\\\
This analysis was tedious and time consuming and it really challenged me. One of my recent projects involved “reverse engineering” a 3rd party code which was accomplished in a time frame of 2 weeks. My team recognized me as the go-to guy for “rapid development and prototype”.\\\\
In my free time, I’m constantly learning new technologies and exploring \& contributing to the open-source community.\\\\
If you require any further information or interview, please do not hesitate to contact me. Thank you very much for your kind consideration.

\end{content}
\sign{Sunil BN}
\end{letter}

\note{Full r\'esum\'e and academic transcripts attached.}

\begin{contactdetails}
\email{}
\github{github.com/sunhick}
\mobilephone{}
\end{contactdetails}


\end{document}
