\begin{category}{Work Experience}
\citem{Graduate Research Assistant}\\
University of Colorado, Boulder~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\textit{Dec 2015 - Present}
\begin{itemize}
    \item {Development of firmware for YPOD(Arduino Yun and chemical sensors) a low cost air quality monitoring system. Supervisor: Prof. Michael Hannigan}
    \item {Developing MongoDB backend using AWS for storing the data streamed by Arduino yun over the WiFi module.}
    \item {Colloboration and integration of YPOD data with OpenAQ, a real-time database that provides programmatic and historical access to air quality data.}\\
\end{itemize}

\citem{Graduate Teaching Assistant}\\
University of Colorado, Boulder~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\textit{Aug 2015 - Dec 2015}
\begin{itemize}
    \item {Taught Data structures in C++11 to undergraduates. Under supervision of Prof. Rick Osborne.}\\
\end{itemize}

\citem{Senior Software Engineer}\\
Siemens Healthcare, Bangalore~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\textit{Jan 2014 - Jul 2015}
\begin{itemize}
     \item {Design, development, Unit testing of software components related to medical imaging software - Syngo.Native( Siemens proprietary software platform for imaging)}
     \item {Design and development of display manager for DICOM image rendering using Direct 3D and WPF.}
     \item {Prototyping of data management module for Imaging software.}\\
\end{itemize}

\citem{Systems Engineer}\\
Siemens Healthcare, Bangalore~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\textit{Jul 2011 - Jan 2014}
\begin{itemize}
    \item {Design, development, unit testing and bug fixing of medical Imaging software.}
    \item {Exploring and incorporating the new algorithms, strategies to meet the performance(Increase by 5\%) and memory(reduced leak of 100 MB/hr) in the product.}
    \item {Knowledge management by documenting details of all software components.}
    \item {Coordinating and Integrating 3rd party software package into sygno.Interventional product.}
    \item {Providing timely trainings and hands on session to the team to keep up with the latest Microsoft technologies (WPF, WCF, PRISM).}\\
\end{itemize}

\end{category}
